Adopting agile software development in the large organizations: A systematic literature review

### 2014-08-13 journal/content.tex
Finishing up on discussion

\subsection{Agile is difficult to implement}

@@

A challenge realting particularly to large scale is that development teams need
to interface with various other organizational functions \citep{Lindvall2004}.
Particular function mentioned are other development teams and requirements
management. \citet{Boehm2005} and also \citet{Cohn2003} mentions human resources
as an additional group.
Our research reflects very closely on the challenges development has in
interfacing with these groups. Our research identified still a number of other
groups that were not mentioned in existing literature (see section
\ref{section_other_functions}).

\citet{Cohn2003} brings up a number of challenges that our research also
discovered.

As a conclusion on the comparison between this study and previous literature it
can be said that there is a very high level of correspondence. However, the
existing publications discussing large scale agile adoption provides very little
grounds for the claims presented. Our research can be considered to groundedly
confirm the claims presented in existing literature.

The majority of transformation related topics presented in existing literature
is found in this research. However, this does not go the other way, as each of
the sources discussed as background is missing some area that this study brings
up.
It should also be noted that the thoroughness of discussion on various topics
differ between this study and the background literature. Therefore each study
will give a different impression on the relative importance of the topics
discussed. In this research the number of sources referring to a particular
topic may be used as an estimate of relative importance.

@@

\section{Conclusion}

>>>>

\subsection{Agile is difficult to implement}
\label{section_difficult_to_implement}

@@

A challenge relating particularly to large scale is that development teams need
to interface with various other organizational functions \citep{Lindvall2004}.
Particular function mentioned are other development teams and requirements
management. \citet{Boehm2005} and also \citet{Cohn2003} mentions human resources
as an additional group.
Our research reflects very closely on the challenges development has in
interfacing with these groups. Our research identified still a number of other
groups that were not mentioned in existing literature (see section
\ref{section_other_functions}).

\citet{Cohn2003} brings up a number of challenges that our research also
discovered, including change resistance, misunderstanding the agile model, and
overzealous teams. Although the topics are the same, the discussion of
\citeauthor{Cohn2003} differ from the results of our research. For instance,
they present the challenge of misunderstanding agile development merely as fear
of micromanagement, whereas our research provides a rich set of examples (see
section \ref{section_difficult_to_implement}).
The discussion on overzealous teams also seems to get disproportionate attention
compared to the groundedness observed in our research.

As a conclusion on the comparison between this study and previous literature it
can be said that there is a very high level of correspondence. However, the
existing publications discussing large scale agile adoption provides very little
grounds for the claims presented. Our research can be considered to confirm the
claims presented in existing literature in a grounded way.

The majority of transformation related topics presented in existing literature
is found in this research. However, this does not go the other way, as each of
the sources discussed as background is missing some area that this study brings
up.
It should also be noted that the extensiveness of discussion on various topics
differ between this study and the background literature. Therefore each study
will give a different impression on the relative importance of the topics
discussed. In this research the number of sources referring to a particular
topic may be used as a grounded estimate on relative importance.

@@

\newpage
\section{Conclusion}
